Programming Assignment 2

### 2015-04-02 paper.tex
Update paper.tex
Filled out performance sections of the Hamming/MAX

\subsection{Image Encoding}
The image encoding... blah blah. Type here

@@

>>>>

\subsection{Image Encoding}
the image encoding blah blah. Type here

@@

\subsection{Performance}
The Hamming/MAX did an excellent job when classifying animals. Both the aquatic classes and the planes had classifications that were completely incorrect, and another that was completely correct. We attribute this half-sided success to the images we selected for testing and for centroid-generation; the animals were distinct enough that we could tell the difference between the centroids when viewing them. The planes were a mess of lines due to poor image selection. The ships had very sporatic images used to train, and the resultant centroid was a mess. 
\subsection{Sensitivity}
This network was very sensitive to noise. Because it was feed-forward and used hamming distance between vectors, the most important thing was literally how many pixels matched up. Because of this, noise was very detrimental to classification accuracy.

\subsection{Comments}
We constructed out Hamming/MAX layer as per instructions of Lab 2. This led us to become extremely confused, as we weren't using a neural network but the linear-algebra equivalent. We didn't really use neurons. We just used applied linear algebra. Regardless, we went forward with the matrix-only implementation and were pretty pleased with the results.

By far the Hamming/Max was easiest for us to break down and implement.
